### 2023-01-01 documentation/paper.tex
FEATURE: Add section for approach and experiments

\cite{Hasinoff2016Burst}

@@

%-------------------------------------------------------------------------
\section{Approach}
\label{sec:approach}
\blindtext

%-------------------------------------------------------------------------
\section{Experiments}
\label{sec:Experiments}
\blindtext

>>>>

@@

%-------------------------------------------------------------------------
\section{Approach}
\label{sec:approach}

The classic manual approach from digital photography is to take three images of the same scene: 
One overexposed, one underexposed, and one normally exposed. These are superimposed in 
post-processing so that the bright areas of the resulting image are not too bright and the 
dark areas are not too dark. This results in an image that not only contains many bright areas, 
but also many dark areas at the same time.

This classical approach will be contrasted with the method described in \ref{sec:related_work}. 
For this purpose, image bursts of the same scene are processed once according to the 
classical method and once according to the method described in \ref{sec:related_work}. To get a good 
comparison, images of stationary and moving objects are taken, both from a tripod and 
handheld.

%-------------------------------------------------------------------------
\section{Experiments}
\label{sec:Experiments}
\cite{Brooks2016git} has implemented the image processing pipeline described in \ref*{sec:related_work}. To do this, 
he uses Halide, a programming language embedded in C++ that allows efficient image processing 
pipelines to be implemented with little effort. Halide itself requires LLVM to compile. 
Unfortunately, the project has not been actively maintained for quite some time and 
since new versions of Halide and LLVM have been released in the meantime, some of which were 
not backwards compatible, the project could not be compiled out of the box. After many hours of 
trial and error, the project was able to compile with version 10 of both Halide and LLVM. 
To get a reproducible executable version of \cite{Brooks2016git}, a Docker image was created that 
contains the application and runs it on container startup.
